On the probability of finding a nonphysical solution through shadowing\footnote{Preprint available at \cite{preprint}}

### 2020-12-08 main.tex
Correct type error
change to general comput phys

\begin{abstract}
This paper proves that shadowing solutions can be almost surely nonphysical.
This finding invalidates the argument that small perturbations in a chaotic system can only have a small impact on its statistical behavior.
This theoretical finding has implications for many applications
in which chaotic mechanics play an important role.
It suggests, for example, that we can control the climate through subtle perturbations. It also suggests that numerical simulations of chaotic dynamics, such as turbulent flows, may fail to predict the true long-term or statistical behavior.
\keywords{Climate \and Chaotic systems \and Numerical simulations \and Turbulence \and Shadowing sensitivity analysis}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\begin{abstract}
This paper proves that shadowing solutions can be almost surely nonphysical.
This finding invalidates the argument that small perturbations in a chaotic system can only have a small impact on its statistical behavior.
This theoretical finding has implications for many applications
in which chaotic mechanics plays an important role.
It suggests, for example, that we can control the climate through subtle perturbations. It also suggests that numerical simulations of chaotic dynamics, such as turbulent flows and global atmosphere and ocean circulation, may fail to predict the true long-term or statistical behavior.
\keywords{Climate \and Chaotic systems \and Numerical simulations \and Turbulence \and Shadowing sensitivity analysis}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
